### 2021-04-19 SupplementaryMaterial/Vita.tex
Updates from Overleaf

Qinkun Bao is a fifth year Ph.D. student at the College of information Sciences
and Technology, The Pennsylvania State University. He is a member of the Software 
System Security Research Lab where he works under the supervision of Dr. Dinghao Wu.
His research interests span reverse engineering, binary analysis, and trusted computations. Before he went to Penn State, he received his bachelor degree in Electronic Engineering and Information Science from University of Science and Technology of China.

>>>>

Qinkun Bao is a fifth-year Ph.D. student at the College of Information Sciences
and Technology, The Pennsylvania State University. He is a member of the Software 
System Security Research Lab, where he works under the supervision of Dr. Dinghao Wu.
His research interests span reverse engineering, binary analysis, and trusted computing. Before he went to Penn State, he received his bachelor's degree in Electronic Engineering and Information Science from University of Science and Technology of China.
